An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-09-13 paper/main.tex
add first version of introduction

\begin{document}
%
\title{An optimization of bidirectional update language based on the idea of reversible computing
 \thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

@@

Points to discuss
\begin{itemize}
\item When will be the deadline of PEPM2020? (mid of October?)
\item Need to change the style file of latex..
\item []

\item current foldr is not efficient? Are there any efficient foldr? Question to Prof. Hu.
\item Language to show semantics: fi?, $f^{-1}$, $cond_{sv}$ and $cond_{s}$
\item A good simple example of bx: Used in explanation of BiGUL and evaluation of pg.
\item Related work: suggest?
\item another pg ?? should be compared?
\end{itemize}

\begin{tabular}{c|c|c}
  {} & {Not to keep eval info} & {Keep eval info as a function}\\ \hline
  {eager evaluation} & {pg} & {cpg}\\ \hline
  {lazy evaluation} & {??} & {kpg}
\end{tabular}

@@

@@

\begin{itemize}
\item Importance of BX, BX is a solution of view update problem in database.
\item Explanation of put-based BX: BiGUL.
\item Current status of BiGUL: Fastest BX language in the world
\item But there is a problem: Efficiency of compose evaluation. The current implementation of BiGUL does not save the intermediate states, the number of get is quadratic. This is not good.
\item To solve this problem we use an idea: introduce pg : combination of put and get. Then, no information will be lost in a specific condition.
%  an idea from reversible computation: not to lose any information.
\item We extend pg with several ideas to produce faster implementation.
\item 
\end{itemize}

@@

\begin{itemize}
\item Improvement of evaluation efficiency
  \begin{itemize}
  \item Quadratic to exponential? 
  \item The introduced extentions (maybe) use more memory than the original approach, but they are faster than the original.
  \end{itemize}
\item Reveal a part of relationship between BX and Reversible.
  \begin{itemize}
  \item Very well-behaved (no adaptive-case) \& The same evaluation path $\to$ No garbage Reversible Computation.
  \item A pair of put and get is self-inverse (involution).
  \item If we can obtain good parameter (dummy) for a BiGUL program,
    put(s, dummy) can be a complement function.
  \end{itemize}

>>>>

\begin{document}
%
\title{An efficient composition of bidirectional programs
  by tupling and lazy updates 
%  tupling
%  accumulating updates = lazy updates
%  based on the idea of reversible computing  
  % \thanks{Supported by organization x.}
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

@@

Points to discuss
\begin{itemize}
\item Schedule:
\item Introduction (story), Contribution, positions, examples, beginning of September?
\item zero draft : mid of September

\item When will be the deadline of PEPM2020 (October 18th)
\item ESOP (?)
\item Need to change the style file of latex..
\item []

\item Related work?
\item

\item TODO: %relationship between result (original vs \{cpg, kpg, xpg\})
%\item right assoc \& Recursive example?
%\item current foldr is not efficient? Are there any efficient foldr? Question to Prof. Hu.
%\item Language to show semantics: fi?, $f^{-1}$, $cond_{sv}$ and $cond_{s}$
%\item A good simple example of bx: Used in explanation of BiGUL and evaluation of pg.
%\item Related work: suggest?
%\item another pg ?? should be compared?
\end{itemize}

@@

%\begin{itemize}
%\item Importance of BX, BX is a solution of view update problem in database.
%\item goodness of 
%\item Explanation of put-based BX: BiGUL.
%\item Current status of BiGUL: Fastest BX language in the world
%\item But there is a problem: Efficiency of compose evaluation. The current implementation of BiGUL does not save the intermediate states, the number of get is quadratic. This is not good.
%\item To solve this problem we use an idea: introduce pg : combination of put and get. Then, no information will be lost in a specific condition.
%  an idea from reversible computation: not to lose any information.
%\item We extend pg with several ideas to produce faster implementation.
%\item 
%\end{itemize}

%\begin{itemize}
%\item Importance of BX, BX is a solution of view update problem in database.
%\item goodness of 
%\item Explanation of put-based BX: BiGUL.
%\item Current status of BiGUL: Fastest BX language in the world
%\item But there is a problem: Efficiency of compose evaluation. The current implementation of BiGUL does not save the intermediate states, the number of get is quadratic. This is not good.
%\item To solve this problem we use an idea: introduce pg : combination of put and get. Then, no information will be lost in a specific condition.
%  an idea from reversible computation: not to lose any information.
%\item We extend pg with several ideas to produce faster implementation.
%\item 
%\end{itemize}

In software, there are strong demands for synchronizing the data. In database community it is known as ``view update problem'' and researched for a long time \cite{}.
% A Survey to View Update Problem 
As a solution for this problem, bidirectional transformation is introduced \cite{}. It enables the evaluation of source updating: ``put'' produces the updated source from the original source and the updated view.
% The first paper of bidirectional transformation

There are two types of bidirectional transformation. One is get-based bidirectional transformation \cite{} that receives the definition of $get$ and provides $put$. A problem of this approach is that it is possible to derive many correct $put$s. To choose one put, hulistics and programmer's intentions are needed. Another approach is put-based bidirectional transformation \cite{} that received the definition of $put$ and provide $get$. From a $put$ we can derive an unique $get$.

BiGUL \cite{} is one of put-based bidirectional transformation language. It is fastest bidirectional language in the world now. However, it contains a problem when the BiGUL programs including many compositions. BiGUL does not store the intermediate states when $get$s are re-evaluated so many times. In this case the number of get is quadratic.

Figure that shows many gets re-evaluation

To solve this problem and make BiGUL evaluation efficient, we use two techniques. The first technique is tupling, well-known technique for efficiency \cite{}. Its basic idea is to reduce the common computations by combining two evaluations. In our work, we combines the evaluation of $put$ and $get$, and introduce $pg$. Thanks to tupling, we do not lose information like intermediate states.
The second technique is lazy update and lazy computation. $pg$ itself includes some inefficiency. For removing the inefficiency we do the update and computation lazily.

The rest of this paper is the following. We introduce a subset of BiGUL, miniBiGUL, and show syntax, semantics, and properties in Section 2. Combining the semantics of put and get in Section 2, we construct $pg$ and show that it is self-inverse in Section 3.
We apply three optimizations to $pg$ in sequence. The first one is keeping update of BX lazily, and obtain $cpg$ in Section 4. The second one is lazy evaluation to avoid redundant computation, and obtain $kpg$ in Section 5. The third one is combination of $pg$ and $kpg$ in Section 6, because they are strong for different type of programs. In Section 7, we show experiemntal result of $pg$, $cpg$, $kpg$, $xpg$ and the original miniBiGUL.
In Section 8 we discuss about related work, and conclude in Section 9.

@@

%\begin{itemize}
%\item Importance of BX, BX is a solution of view update problem in database.
%\item Explanation of put-based BX: BiGUL.
%\item Current status of BiGUL: Fastest BX language in the world
%\item But there is a problem: Efficiency of compose evaluation. The current implementation of BiGUL does not save the intermediate states, the number of get is quadratic. This is not good.
%\item To solve this problem we use an idea: introduce pg : combination of put and get. Then, no information will be lost in a specific condition.
%  an idea from reversible computation: not to lose any information.
%\item We extend pg with several ideas to produce faster implementation.
%\item 
%\end{itemize}

@@

\begin{itemize}
\item Improvement of evaluation efficiency
  \begin{itemize}
  \item Quadratic to exponential? 
  \item The introduced extentions (maybe) use more memory than the original approach, but they are faster than the original.
  \end{itemize}
\item Tupling is also effective in bidirectional programming.
  \begin{itemize}
  \item A pair of put and get is self-inverse (involution).
  \end{itemize}
\item lazy update \& lazy computation is also good optimization for BX.
%\item Reveal a part of relationship between BX and Reversible.
%  \begin{itemize}
%  \item Very well-behaved (no adaptive-case) \& The same evaluation path $\to$ No garbage Reversible Computation.
%  \item 
%  \item If we can obtain good parameter (dummy) for a BiGUL program,
%    put(s, dummy) can be a complement function.
  \end{itemize}
